### 2021-01-26 Phys 311/main.tex
Upload

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Title Page
% LaTeX Template
% Version 2.0 (17/7/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (LaTeX - Title Creation) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
% Instructions for using this template:
% This title page is capable of being compiled as is. This is not useful for 
% including it in another document. To do this, you have two options: 
%
% 1) Copy/paste everything between \begin{document} and \end{document} 
% starting at \begin{titlepage} and paste this into another LaTeX file where you 
% want your title page.
% OR
% 2) Remove everything outside the \begin{titlepage} and \end{titlepage}, rename
% this file and move it to the same directory as the LaTeX file you wish to add it to. 
% Then add \input{./<new filename>.tex} to your LaTeX file where you want your
% title page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article}

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{mathpazo} % Palatino font
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{float}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here

	\center % Centre everything on the page

	%------------------------------------------------
	%	Headings
	%------------------------------------------------

	\textsc{\LARGE University of Washington, Bothell}\\[1.5cm] % Main heading such as the name of your university/college

	\textsc{\Large CTA Term Paper}\\[0.5cm] % Major heading such as project name

	\textsc{\large B Phys 311, Intro to Astrophysics}\\[0.5cm] % Minor heading such as course title

	%------------------------------------------------
	%	Title
	%------------------------------------------------

	\HRule\\[0.4cm]

	{\huge\bfseries Segue 1: An Unevolved Fossil Galaxy from the Early Universe}\\[0.4cm] % Title of your document

	\HRule\\[1.5cm]

	%------------------------------------------------
	%	Author(s)
	%------------------------------------------------

	\begin{minipage}{0.4\textwidth}
		\begin{flushleft}
			\large
			\textit{Pongpak Techagumthorn}\\
			\textsc{pongpakt@uw.edu} % Your name
		\end{flushleft}
	\end{minipage}

	%------------------------------------------------
	%	Date
	%------------------------------------------------

	\vfill\vfill\vfill % Position the date 3/4 down the remaining page

	{\large January 25, 2021} % Date, change the \today to a set date if you want to be precise

	%------------------------------------------------
	%	Logo
	%------------------------------------------------

	%\vfill\vfill
	%\includegraphics[width=0.2\textwidth]{placeholder.jpg}\\[1cm] % Include a department/university logo - this will require the graphicx package

	%----------------------------------------------------------------------------------------

	\vfill % Push the date up 1/4 of the remaining page

\end{titlepage}

%----------------------------------------------------------------------------------------

\section{Description}
This is a test
Hiring Professionals (KajLagbe) is a platform for publishing and finding jobs that are not so conventional to the existing job marketplace. We focus on providing manpower specially for the day to day requirements.
\newline 
\newline
So, there are specially two types of user that will use this platform. One of them will be the Professionals with actual skills and the other type of the user will be the Consumer who will consume the service.
\newline
\newline
Consumers can post jobs specifying the skill that is needed for the job.
Professionals can provide their skills during registration, which will be the key to finding all of the available jobs. Professionals can also search jobs based on location.
\newline
\newline
When professionls see a job post s/he can comment on the post to seek the attention of the consumer. Then comment is posted successfully s/he will be regarded as an interested user and option will be available to consumer to submit contract to the professional. Multiple professionals can be interested. Consumer can choose among them based on their rating / skill / daily charge.
\newline
\newline
When contract is submitted to a professional, the contract will be visible to the contracts page of the professional. If a professional accepts the contract the job will be restricted for all other users to accept.
\newline
\newline
When a professional completes a job he will have to press Job Completed button which will generate the receipt with the bill. Professionals can then rate the consumer or return to home page. In the same way consumers will also get an option to rate the professional who has completed his job.

\clearpage

\section{Motivation}
The motivation behind this project was the thought that, if there was a platform where we can find the workers needed for our day to day living. If we needed an electrician we don't have to go looking for an electrician but the only thing that we have to do is just make a post, where many professionals (electrician) can find you and have your work done with the best price.
\clearpage

\section{Novelty}

What is new about this project?

\begin{itemize}
\item Get jobs that are posted daily
\item Get only the job suggestions that match your skills
\item Manage post and contracts more efficiently
\item Bill is calculated on daily basis
\end{itemize}

\clearpage

\section{Sample Picture}
\includegraphics[scale=0.5]{Untitled+design+(2).png}

\clearpage

\section{Tools Used}

\begin{table}[H]
\centering
\caption{Tools used for the project}
\label{my-label}
\begin{tabular}{|l|l|}
\hline
\textbf{Tool} & \textbf{Purpose}         \\ \hline
Xampp         & For creating a localhost \\ \hline
phpMyAdmin    & For hosting the database \\ \hline
MySQL    	  & As a database system \\ \hline
PHP    		  & For server side handling \\ \hline
Javascript    & For AJAX call and form validation \\ \hline
Bootstrap     & For responsive interface \\ \hline
CSS \& HTML   & For designing basic template \\ \hline
\end{tabular}
\end{table}

\clearpage

\section{Challenges Faced}
These are the challenges we faced while doing the project:
\begin{itemize}
\item \textbf{Challenge 1: } While implementing auto-complete we couldn't get data dynamically.
\item \textbf{Challenge 2: } Mailing with PHPMailer didn't work at first due to authorization problem and some protocols.
\item \textbf{Challenge 3: } Sending/receiving data in the background with AJAX was quite confusing at first.
\item \textbf{Challenge 4: } Calculating fare based on time interval was tough to implement at first.
\end{itemize}

\clearpage

\section{Applications}

Applications of our project is as follows:
\begin{itemize}
\item \textbf{Application 1: } Find jobs based on skills and place.
\item \textbf{Application 2: } Get suggestions of daily jobs that match your skills.
\item \textbf{Application 3: } Get the list of all of your contracts that are currently in place.
\item \textbf{Application 4: } Keep track of your completed jobs along with the earnings.
\item \textbf{Application 5: } Posting jobs that requires a specific skill
\item \textbf{Application 6: } Get the list of top employers
\item \textbf{Application 7: } Generate receipt based on the time duration of a service
\item \textbf{Application 8: } Comment on posts published by consumers
\item \textbf{Application 9: } Rating enabled for consumers and professionals when job is finished
\item \textbf{Application 10: } Each user have their own profile with all of their basic information, professionals have their skills also

\end{itemize}

\clearpage

\section{Future Work}
\begin{itemize}
\item Develop a mobile application based on this project.
\item Adding support for map for direction and estimated time of arrival.
\item One click to call feature.
\item Enabling professionals active time period.
\item Enabling individual messaging and replying to comments.
\item Adding automated fare calculation based on some factor (e.g. time, distance).
\item Discount will be provided to consumers.
\end{itemize}

\clearpage

\end{document}

### 2021-01-30 Phys 311/CTA Paper/main.tex
Move folder

--- 2021-01-26 Phys 311/main.tex
@@
 
-	\textsc{\Large CTA Term Paper}\\[0.5cm] % Major heading such as project name
+	\textsc{\Large CTA Proposal}\\[0.5cm] % Major heading such as project name
 
@@
 
-	%------------------------------------------------
-	%	Logo
-	%------------------------------------------------
-
-	%\vfill\vfill
-	%\includegraphics[width=0.2\textwidth]{placeholder.jpg}\\[1cm] % Include a department/university logo - this will require the graphicx package
-
-	%----------------------------------------------------------------------------------------
-
 	\vfill % Push the date up 1/4 of the remaining page
@@
 
-\section{Description}
-This is a test
-Hiring Professionals (KajLagbe) is a platform for publishing and finding jobs that are not so conventional to the existing job marketplace.
-We focus on providing manpower specially for the day to day requirements.
-\newline 
-\newline
-So, there are specially two types of user that will use this platform.
-One of them will be the Professionals with actual skills and the other type of the user will be the Consumer who will consume the service.
-\newline
-\newline
-Consumers can post jobs specifying the skill that is needed for the job.
-Professionals can provide their skills during registration, which will be the key to finding all of the available jobs. Professionals can also search jobs based on location.
-\newline
-\newline
-When professionls see a job post s/he can comment on the post to seek the attention of the consumer.
-Then comment is posted successfully s/he will be regarded as an interested user and option will be available to consumer to submit contract to the professional.
-Multiple professionals can be interested.
-Consumer can choose among them based on their rating / skill / daily charge.
-\newline
-\newline
-When contract is submitted to a professional, the contract will be visible to the contracts page of the professional.
-If a professional accepts the contract the job will be restricted for all other users to accept.
-\newline
-\newline
-When a professional completes a job he will have to press Job Completed button which will generate the receipt with the bill.
-Professionals can then rate the consumer or return to home page.
-In the same way consumers will also get an option to rate the professional who has completed his job.
-
-\clearpage
+\section{Topic Background}
 
@@
 
-Applications of our project is as follows:
-\begin{itemize}
-\item \textbf{Application 1: } Find jobs based on skills and place.
-\item \textbf{Application 2: } Get suggestions of daily jobs that match your skills.
-\item \textbf{Application 3: } Get the list of all of your contracts that are currently in place.
-\item \textbf{Application 4: } Keep track of your completed jobs along with the earnings.
-\item \textbf{Application 5: } Posting jobs that requires a specific skill
-\item \textbf{Application 6: } Get the list of top employers
-\item \textbf{Application 7: } Generate receipt based on the time duration of a service
-\item \textbf{Application 8: } Comment on posts published by consumers
-\item \textbf{Application 9: } Rating enabled for consumers and professionals when job is finished
-\item \textbf{Application 10: } Each user have their own profile with all of their basic information, professionals have their skills also
-
-\end{itemize}
-
 \clearpage

### 2021-01-31 Phys 311/CTA Paper/main.tex
Content

@@
 \documentclass[11pt]{article}
+\usepackage{geometry}
+ \geometry{
+ letterpaper,
+ total={7.25 in, 9.375 in},
+ left=0.625 in,
+ top=0.875 in,
+ headsep=14 pt,
+ headheight=14 pt,
+ }
+
+\usepackage{fancyhdr}
+ \pagestyle{fancy}
+ \fancyhf{}
+ \lhead{CTA Proposal}
+ \rhead{SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}
+ \rfoot{Techagumthorn \thepage}
 
@@
 \usepackage{float}
+\usepackage{amssymb}
 
@@
 
-	{\huge\bfseries Segue 1: An Unevolved Fossil Galaxy from the Early Universe}\\[0.4cm] % Title of your document
+	{\huge\bfseries SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}\\[0.4cm] % Title of your document
 
@@
 \section{Topic Background}
+When studying the early universe scientists commonly seek out stars with low metal content. Locked inside these stars
+is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
+these stars, specifically low $\left[ Fe / H \right]$ values and high $\left[ \alpha / Fe \right]$ values, indicate that
+the stars were formed in the early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the
+timescales of nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements are carbon, oxygen, neon,
+magnesium, silicon, sulfur, argon, and calcium.
 
-\section{Motivation}
-The motivation behind this project was the thought that, if there was a platform where we can find the workers needed for our day to day living.
-If we needed an electrician we don't have to go looking for an electrician but the only thing that we have to do is just make a post, where many professionals (electrician) can find you and have your work done with the best price.
-\clearpage
+The earliest supernovae events in the universe were core-collapse supernovae of Massive stars. Massive stars produce large
+amounts of $\alpha$-elements during their stellar evolution and core-collapse explosion. Massive stars have short lifetimes
+of less than 10 million years. Heavy metals, such as iron, appeared later in the astronomical timeline as a byproduct of Type Ia
+supernovae. Type Ia supernovae originate from binary star systems containing a white dwarf stars. These binary systems have much
+longer lifetimes, on the order of $10^8$ years, before collapsing into a supernova. These substantially different timelines allow
+scientists to approximately date the relative timing of nucleosynthesis in early stars.
+
+For decades scientists looked at low metal stars in the halo of the Milky Way to study the early universe. In the past decade efforts
+such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal (dSph) galaxies and ultra faint dwarfs
+with total luminosities in the range of \(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\),
+respectively. Within this pool of dSph and ultra faint dwarf galaxies scientists discovered a small handful of ultra faint dwarf galaxies
+that showed extremely low $\left[ Fe / H \right]$ values. In this small handful one galaxy, SEGUE 1 stood out from the rest.
+SEGUE 1 stood out since it's stars show increasing metallicity but do not exhibit decreasing $\left[\alpha / Fe\right]$ ratios.
+This would indicate that SEGUE 1 dates back to the very early universe predating Type Ia supernovae events.
 
@@
 
-What is new about this project?
+The authors of this paper made new spectrography measurements of 6 stars within SEGUE 1 focusing on the chemical enrichment process
+to better understand star formation in the very early universe.
 
-\begin{itemize}
-\item Get jobs that are posted daily
-\item Get only the job suggestions that match your skills
-\item Manage post and contracts more efficiently
-\item Bill is calculated on daily basis
-\end{itemize}
+\section{Future Work}
 
@@
 
-\section{Sample Picture}
-\includegraphics[scale=0.5]{Untitled+design+(2).png}
-
-\clearpage
-
-\section{Tools Used}
-
-\begin{table}[H]
-\centering
-\caption{Tools used for the project}
-\label{my-label}
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Tool} & \textbf{Purpose}         \\ \hline
-Xampp         & For creating a localhost \\ \hline
-phpMyAdmin    & For hosting the database \\ \hline
-MySQL    	  & As a database system \\ \hline
-PHP    		  & For server side handling \\ \hline
-Javascript    & For AJAX call and form validation \\ \hline
-Bootstrap     & For responsive interface \\ \hline
-CSS \& HTML   & For designing basic template \\ \hline
-\end{tabular}
-\end{table}
-
-\clearpage
-
-\section{Challenges Faced}
-These are the challenges we faced while doing the project:
-\begin{itemize}
-\item \textbf{Challenge 1: } While implementing auto-complete we couldn't get data dynamically.
-\item \textbf{Challenge 2: } Mailing with PHPMailer didn't work at first due to authorization problem and some protocols.
-\item \textbf{Challenge 3: } Sending/receiving data in the background with AJAX was quite confusing at first.
-\item \textbf{Challenge 4: } Calculating fare based on time interval was tough to implement at first.
-\end{itemize}
-
-\clearpage
-
-\section{Applications}
-
-\clearpage
-
-\section{Future Work}
-\begin{itemize}
-\item Develop a mobile application based on this project.
-\item Adding support for map for direction and estimated time of arrival.
-\item One click to call feature.
-\item Enabling professionals active time period.
-\item Enabling individual messaging and replying to comments.
-\item Adding automated fare calculation based on some factor (e.g. time, distance).
-\item Discount will be provided to consumers.
-\end{itemize}
-
-\clearpage
+\section{References}
 

### 2021-02-01 Phys 311/CTA Paper/report.tex
report finished

%% Beginning of file 'sample63.tex'
%%
%% Modified 2019 June
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.3 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.3
\documentclass{aastex63}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex63}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex63}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\aastex}{AAS\TeX}
\newcommand{\latex}{La\TeX}

%% For manuscript that include authors in collaborations, AASTeX v6.3
%% builds on the \collaboration command to allow greater freedom to 
%% keep the traditional author+affiliation information but only show
%% subsets. The \collaboration command now must appear AFTER the group
%% of authors in the collaboration and it takes TWO arguments. The last
%% is still the collaboration identifier. The text given in this
%% argument is what will be shown in the manuscript. The first argument
%% is the number of author above the \collaboration command to show with
%% the collaboration text. If there are authors that are not part of any
%% collaboration the \nocollaboration command is used. This command takes
%% one argument which is also the number of authors above to show. A
%% dashed line is shown to indicate no collaboration. This example manuscript
%% shows how these commands work to display specific set of authors 
%% on the front page.
%%
%% For manuscript without any need to use \collaboration the 
%% \AuthorCollaborationLimit command from v6.2 can still be used to 
%% show a subset of authors.
%
%\AuthorCollaborationLimit=2
%
%% will only show Schwarz & Muench on the front page of the manuscript
%% (assuming the \collaboration and \nocollaboration commands are
%% commented out).
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{SEGUE 1}
\shortauthors{Techagumthorn}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.3 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% argument which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
%% present or in the LaTeX pathway, the OrcID icon will appear next to
%% the authors name.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.3 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.3 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Pongpak Techagumthorn}
\email{pongpakt@uw.edu}

\author{Pongpak Techagumthorn}
\affiliation{University of Washington Bothell}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.3 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment.

% \begin{abstract}

% 	This is an abstract

% \end{abstract}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Topic Background} \label{sec:background}

When studying the early universe scientists commonly seek out stars with low metal content. Locked inside these stars
is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
these stars, specifically low [ Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the 
early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the timescales of 
nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements are carbon, oxygen, neon, 
magnesium, silicon, sulfur, argon, and calcium.

The earliest supernovae events in the universe were core-collapse supernovae of Massive stars. Massive stars produce large
amounts of $\alpha$-elements during their stellar evolution and core-collapse explosion. Massive stars have short lifetimes
of less than 10 million years. Heavy metals, such as iron, appeared later in the astronomical timeline as a byproduct of 
Type Ia supernovae. Type Ia supernovae originate from binary star systems containing a white dwarf stars. These binary 
systems have much longer lifetimes, on the order of $10^8$ years, before collapsing into a supernova. These substantially 
different timelines allow scientists to approximately date the relative timing of nucleosynthesis in early stars.

For decades scientists looked at low metal stars in the halo of the Milky Way to study the early universe. In the past decade 
efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal (dSph) galaxies and 
ultra faint dwarfs with total luminosities in the range of \(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and 
\(L \lesssim 10^5 L_{\odot}\), respectively. Within this pool of dSph and ultra faint dwarf galaxies scientists discovered 
a small handful of ultra faint dwarf galaxies that showed extremely low [Fe/H] values. In this small handful one galaxy, 
SEGUE 1 stood out from the rest. SEGUE 1 stood out since it's  stars show increasing metallicity but do not exhibit decreasing
[$\alpha$/Fe] ratios. This would indicate that SEGUE 1 dates back to the very early universe predating Type Ia supernovae events.

\section{Novelty} \label{sec:novelty}

The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the MIKE spectrograph focusing on 
the chemical enrichment process to better understand star formation in the very early universe. The six stars that were chosen 
were the brightest stars in SEGUE 1 which allowed for high resolution spectrography.

\section{Results, Discussion, and Future Work} \label{sec:dicussion}

Using the MIKE spectrograph the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, 
neutron-capture elements, and other lighter elements. The authors then compared this data to stars found in classical dSph 
galaxies and the Milky Way halo and concluded that SEGUE 1 is a surviving first galaxy with only one round of star formation. In
the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable 
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing 
metallicity and increasing iron abundance. This indicated that there was only one Type Ia supernova that enriched SEGUE. This 
contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing 
iron abundance as they evolve alongside energetic supernovae events. Other indications of the age of SEGUE include enhanced
[$\alpha$/Fe] values found in all it's stars that are consistent with their birth cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

Future research points to observing a larger portion of SEGUE 1 stars. The six stars that were observed in this paper were deemed to
be the brightest in the ultra faint dwarf galaxy and only allowed for a moderate S/N values between 20 and 46. In order to observe the other, dimmer,
stars in SEGUE 1 we would require better telescopes to overcome the noise.

%% For this sample we use BibTeX plus aasjournals.bst to generate the
%% the bibliography. The sample63.bib file was populated from ADS. To
%% get the citations to show in the compiled file do the following:
%%
%% pdflatex sample63.tex
%% bibtext sample63
%% pdflatex sample63.tex
%% pdflatex sample63.tex

\nocite{*}
\bibliography{bibliography}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample63.tex'.

### 2021-03-02 Phys 311/CTA/Paper/paper.tex
add paper
progress

--- 2021-02-01 Phys 311/CTA Paper/report.tex
@@
 
-\title{SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}
+\title{CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}
 
@@
 is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
-these stars, specifically low [ Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the 
+these stars, specifically low [Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the
 early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the timescales of
-nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements are carbon, oxygen, neon, 
-magnesium, silicon, sulfur, argon, and calcium.
+nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements that the authors are interested 
+in are carbon, oxygen, neon, magnesium, silicon, sulfur, argon, and calcium.
 
@@
 
-\section{Novelty} \label{sec:novelty}
+\section{Novelty and Methods} \label{sec:novelty}
 
-The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the MIKE spectrograph focusing on 
-the chemical enrichment process to better understand star formation in the very early universe. The six stars that were chosen 
-were the brightest stars in SEGUE 1 which allowed for high resolution spectrography.
+The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the Magellan/MIKE and Keck/HIRES
+spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
+stars that were chosen were the brightest stars in SEGUE 1 which allowed for high resolution spectrography. Using the spectrographs
+the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, neutron-capture elements, and other 
+lighter elements. The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
+The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
+noise ratio (S/N) was only moderate with values between 20 and 50
 
@@
 
-Using the MIKE spectrograph the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, 
-neutron-capture elements, and other lighter elements. The authors then compared this data to stars found in classical dSph 
-galaxies and the Milky Way halo and concluded that SEGUE 1 is a surviving first galaxy with only one round of star formation. In
-the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable 
+With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
+
+In the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable
 from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing

### 2021-03-03 Phys 311/CTA/Paper/paper.tex
first draft

@@
 
-When studying the early universe scientists commonly seek out stars with low metal content. Locked inside these stars
-is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
-these stars, specifically low [Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the
-early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the timescales of
-nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements that the authors are interested 
-in are carbon, oxygen, neon, magnesium, silicon, sulfur, argon, and calcium.
+When studying the early universe scientists commonly seek out stars that were formed early on in the universe.
+Locked inside these stars are clues about the physical and chemical conditions that led to the formation of the star.
+With this information scientists can better understand physical and chemical conditions in the early universe as a whole.
+One way to identify these ancient stars is by their relatively low heavy metal $\left(Z \geq 24\right)$ content compared to
+lighter elements, such as $\alpha$-process elements and hydrogen.
 
-The earliest supernovae events in the universe were core-collapse supernovae of Massive stars. Massive stars produce large
-amounts of $\alpha$-elements during their stellar evolution and core-collapse explosion. Massive stars have short lifetimes
-of less than 10 million years. Heavy metals, such as iron, appeared later in the astronomical timeline as a byproduct of
-Type Ia supernovae. Type Ia supernovae originate from binary star systems containing a white dwarf stars. These binary
-systems have much longer lifetimes, on the order of $10^8$ years, before collapsing into a supernova. These substantially
-different timelines allow scientists to approximately date the relative timing of nucleosynthesis in early stars.
+Lighter $\alpha$-elements are synthesized within massive stars and are released into the interstellar medium (ISM) once these
+massive stars undergo core-collapse supernova upon running out of helium. The lifetime of these massive stars, from their
+nucleosynthesis to their core collapse supernova event takes place in a very short time frame, often less than $10^{6}$ yrs.
+Heavier elements, the paper specifically measures iron (FeI and FeII), strontium, and barium abundance, are synthesized
+and released later in the universe timeline. Iron is mainly synthesized during Type Ia supernovae events. These events occur
+when a white dwarf in a binary star system reaches the critical Chandrasekhar limit and explodes into a supernova event.
+These white dwarf systems have much longer lifetimes of around $10^{8}$ yrs.
+Strontium and Barium, unlike the $\alpha$-elements and iron do not form via normal fusion but only during neutron capture
+nucleosynthesis. Neutron capture nucleosynthesis happens during r-process supernovae and during the nucleosynthesis of
+population III supermassive stars. During each of these neutron capture nucleosynthesis events approximately
+$10^{-4} M_\odot$ of neutron capture elements are released into the ISM.
 
-For decades scientists looked at low metal stars in the halo of the Milky Way to study the early universe. In the past decade
-efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal (dSph) galaxies and
-ultra faint dwarfs with total luminosities in the range of \(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and
-\(L \lesssim 10^5 L_{\odot}\), respectively. Within this pool of dSph and ultra faint dwarf galaxies scientists discovered
-a small handful of ultra faint dwarf galaxies that showed extremely low [Fe/H] values. In this small handful one galaxy,
-SEGUE 1 stood out from the rest. SEGUE 1 stood out since it's stars show increasing metallicity but do not exhibit decreasing
-[$\alpha$/Fe] ratios. This would indicate that SEGUE 1 dates back to the very early universe predating Type Ia supernovae events.
+The low metallicity of early stars, specifically stars with high [$\alpha$/Fe] and low [Fe/H] values, indicate that their
+nucleosynthesis occurred during a period after the first round of core-collapse supernovae but before large numbers of
+Type Ia supernovae events. For decades scientists looked early stars in the halo of the Milky Way to study the early universe.
+These Milky Way halo stars have [Fe/H] values of $< -1.0$.
+
+In the past decade efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal
+(dSph) galaxies and ultra faint dwarfs. These dSph and ultra faint dwarfs have total luminosities in the range of
+\(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\), respectively, which contain
+stars with [Fe/H] values of $\sim -2.5$. With the use of medium resolution spectroscopy scientists recently uncovered a
+moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
+scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE 1, stood out from the rest. 
+SEGUE 1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
+[$\alpha$/Fe] ratios. 
+This would indicate that the star formation phase in SEGUE 1 occurred before most, if not all, Type Ia supernovae events. This
+also indicates that there was likely only one star formation phase within the galaxy.
 
@@
 stars that were chosen were the brightest stars in SEGUE 1 which allowed for high resolution spectrography. Using the spectrographs
-the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, neutron-capture elements, and other 
-lighter elements. The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
+the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
+The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
 The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
@@
 With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
+In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
+and the very bright, and much younger, Arcturus.
 
-In the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable
+In the three lowest metallicity stars (The top 3 blue lines) the abundance of iron (both Fe I and Fe II) is mostly indistinguishable
 from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
-metallicity and increasing iron abundance. This indicated that there was only one Type Ia supernova that enriched SEGUE. This
+iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most one or maybe two Type Ia supernova that enriched SEGUE. This
 contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing

### 2021-03-04 Phys 311/CTA/Paper/paper.tex
update to aastex631

@@
 %%
-%% using aastex version 6.3
-\documentclass{aastex63}
+%% using aastex version 6.3.1
+\documentclass{aastex631}
 
@@
 from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
-iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most one or maybe two Type Ia supernova that enriched SEGUE. This
-contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing
-iron abundance as they evolve alongside energetic supernovae events. Other indications of the age of SEGUE include enhanced
-[$\alpha$/Fe] values found in all it's stars that are consistent with their birth cloud, and the low abundance of neutron-capture
+iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most
+one or maybe two Type Ia supernova that enriched SEGUE. This
+contrasts the trend found in younger galaxies where there would be a clear trend in increasing metallicity and increasing
+iron abundance in the stellar population as they evolve alongside energetic supernovae events.
+
+Other indications of the age of SEGUE include enhanced [$\alpha$/Fe] values found in all it's stars that are consistent with the birth 
+cloud, and the low abundance of neutron-capture
 elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched

### 2021-03-12 Phys 311/CTA/Paper/paper.tex
Content

@@
 
-\title{CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}
+\title{CTA Proposal:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}
 
@@
 moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
-scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE 1, stood out from the rest. 
-SEGUE 1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
+scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE-1, stood out from the rest. 
+SEGUE-1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
 [$\alpha$/Fe] ratios. 
-This would indicate that the star formation phase in SEGUE 1 occurred before most, if not all, Type Ia supernovae events. This
+This would indicate that the star formation phase in SEGUE-1 occurred before most, if not all, Type Ia supernovae events. This
 also indicates that there was likely only one star formation phase within the galaxy.
@@
 
-The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the Magellan/MIKE and Keck/HIRES
+The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
 spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
-stars that were chosen were the brightest stars in SEGUE 1 which allowed for high resolution spectrography. Using the spectrographs
+stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
 the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
@@
 In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
-and the very bright, and much younger, Arcturus.
+and the very bright, and much younger, Arcturus. The plots are listed in ascending order of metallicity from top to bottom.
+
+%% Figure of spectra
 
@@
 from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
-iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most
-one or maybe two Type Ia supernova that enriched SEGUE. This
+iron abundance and increasing metallicity, indicated by the appearance of more spectral lines as the metallicity increases.
+This indicated that there was at most one or maybe two Type Ia supernova that enriched SEGUE-1's birth cloud. This
 contrasts the trend found in younger galaxies where there would be a clear trend in increasing metallicity and increasing
@@
 
-Other indications of the age of SEGUE include enhanced [$\alpha$/Fe] values found in all it's stars that are consistent with the birth 
-cloud, and the low abundance of neutron-capture
-elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
-the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
+%% Fig of [X/Fe] vs [Fe/H]
+
+Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with each other
+and the initial birth cloud. Figure 3 shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe], for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars.
+The top plot in fig. 3 shows the general trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
+The middle plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
+the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. 3 shows the enrichment behavior plot for dSph galaxy
+stars (small black circles), the measured stars from SEGUE-1 (large red filled in circles from this article, and red crosshair from
+previous papers), and some other candidate stars (blue square, green circles, and magenta circles). In this bottom plot we can see that
+the classical dSph stars and some of the other candidate stars have a plateau but do slope down towards the [$\alpha$/Fe] = 0 line.
+On the other hand, the 6 measured stars from SEGUE-1 all reside around the [$\alpha$/Fe] = 0.5 line, even past the point where MW
+Halo starts to slope down on the [Fe/H] axis. The consistent [$\alpha$/Fe] values in SEGUE-1 stars suggest that after the initial
+enrichment of the birth cloud there were no other enrichment events, such as type Ia supernovae, in SEGUE-1.
+
+%% Fig of Enrichment Behavior
+
+The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars,
 which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
@@
 \end{document}
-
-% End of file `sample63.tex'.

### 2021-03-13 Phys 311/CTA/Paper/paper.tex
Add Figures

@@
 \documentclass{aastex631}
+
+%% For wrapping figures in text
+\usepackage{wrapfig}
 
@@
 
-\title{CTA Proposal:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}
+\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}
 
@@
 Type Ia supernovae events. For decades scientists looked early stars in the halo of the Milky Way to study the early universe.
-These Milky Way halo stars have [Fe/H] values of $< -1.0$.
+These Milky Way (MW) Halo stars have [Fe/H] values of $< -1.0$.
 
@@
 also indicates that there was likely only one star formation phase within the galaxy.
-
 \section{Novelty and Methods} \label{sec:novelty}
@@
 The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
-The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
+The detail for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
 noise ratio (S/N) was only moderate with values between 20 and 50
 
-\section{Results, Discussion, and Future Work} \label{sec:dicussion}
+\begin{table}[!h]
+    \includegraphics[width=\textwidth]{obs_detail.png}
+    \caption{Observing details for the six measured stars}
+    \label{table:obs_detail}
+\end{table}
+
+\section{Results and Discussion} \label{sec:dicussion}
 
@@
 
-%% Figure of spectra
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.85\textwidth]{spectra.png}
+    \caption{Spectra of the six stars, in blue, bracketed by $CD -38^{\circ}245$ at the top and Arcturus at the bottom.
+    the spectral lines of the elements are labeled at the bottom with the corresponding ranges of wavelengths.}
+    \label{fig:spectra}
+\end{figure}
 
@@
 
-%% Fig of [X/Fe] vs [Fe/H]
+Using the spectrography data the authors also plotted abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
+that were measured. The dashed line at [X/Fe] = 0 indicates the ratio of the element in our Sun with positive values meaning higher
+abundance and lower values indicating lower abundance, on a log scale. Notice that in all of the SEGUE-1 stars the abundance of
+$\alpha$-elements such as Mg, Si, Ca, and Ti, are all above that of the Sun. Elements that are synthesized by other processes that
+occur later in the timeline such as Al, Cr, and Mn, have consistent abundances lower than that of the Sun.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{elements.jpg}
+    \caption{The abundance ratios [X/Fe] compared to the metallicity [Fe/H] of each of the elements that were measured with
+    the spectroscopes. The six small red circles represent the SEGUE-1 stars measured in this article. The larger red circle
+    is a SEGUE-1 star measured in a previous paper. The small black and blue circles represent MW halo stars measured from
+    previous papers.}
+    \label{fig:elements}
+\end{figure}
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{enrich.jpg}
+    \caption{Enrichment Behavior plots for MW Halo stars, the six measured SEGUE-1 stars, a previously measured SEGUE-1 star,
+    and stars from other classical dSph galaxies. These plots show the relationship between $\alpha$-element abundance (specifically
+    Mg, Ca \& Ti) ratios [$\alpha$/Fe] and the metallicity [Fe/H] within the stars.}
+    \label{fig:enrich}
+\end{figure}
 
@@
 
-%% Fig of Enrichment Behavior
+\begin{wrapfigure}{r}{0.4\textwidth}
+    \begin{center}
+        \includegraphics[width=0.38\textwidth]{neutron_cap.jpg}
+    \end{center}
+    \caption{Birds}
+    \label{fig:neutron_cap}
+\end{wrapfigure}
 
@@
 process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.
+
+\section{Future Work} \label{sec:future}
 

### 2021-03-13 Phys 311/CTA/Paper/paper.tex
Final Draft. Maybe?

@@
 
-\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}
+\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe - Frebel, Simon \& Kirby}
 
@@
 
-\section{Topic Background} \label{sec:background}
+\section{Background} \label{sec:background}
 
@@
 
+\begin{wrapfigure}{r}{0.3\textwidth}
+    \begin{center}
+        \includegraphics[width=0.29\textwidth]{location.jpg}
+    \end{center}
+    \caption{Black dots show the location of surveyed stars within SEGUE-1. The seven dots with red borders indicate the six stars
+    observed in this study as well as one star that was observed in a previous study}
+    \label{fig:loc}
+\end{wrapfigure}
+
 The low metallicity of early stars, specifically stars with high [$\alpha$/Fe] and low [Fe/H] values, indicate that their
@@
 
-The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
+The authors of this paper made new spectrography measurements of six stars within SEGUE-1, highlighted in figure ~\ref{fig:loc},
+ using the Magellan/MIKE and Keck/HIRES
 spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
@@
 With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
-In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
+In figure ~\ref{fig:spectra} the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
 and the very bright, and much younger, Arcturus. The plots are listed in ascending order of metallicity from top to bottom.
@@
 
-Using the spectrography data the authors also plotted abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
+Using the spectrography data the authors also plotted in figure ~\ref{fig:elements} the abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
 that were measured. The dashed line at [X/Fe] = 0 indicates the ratio of the element in our Sun with positive values meaning higher
@@
 
-Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with each other
-and the initial birth cloud. Figure 3 shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe], for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars.
-The top plot in fig. 3 shows the general trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
-The middle plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
-the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. 3 shows the enrichment behavior plot for dSph galaxy
+Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with 
+each other and the initial birth cloud. Figure ~\ref{fig:enrich} shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe],
+for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars. The top left plot in fig. ~\ref{fig:enrich} shows the general 
+trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
+The top right plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
+the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. ~\ref{fig:enrich} shows the enrichment behavior plot for dSph galaxy
 stars (small black circles), the measured stars from SEGUE-1 (large red filled in circles from this article, and red crosshair from
@@
     \end{center}
-    \caption{Birds}
+    \caption{Neutron-capture element abundance [Sr/H] and [Ba/H] within the six observed SEGUE-1 stars in this study 
+    (filled in red circles), one previously studied SEGUE-1 star (empty red circle), MW Halo stars (small black dots),
+    and the other candidate stars (cyan, green, and blue markers). The light dotted line at [X/H] = 0 represents the abundance
+    of the respective element within the sun and the bold dashed line represents the average abundance of the respective element
+    within the observed SEGUE-1 stars.}
     \label{fig:neutron_cap}
@@
 
-The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars,
-which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
-process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.
+The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars.
+Outside of binary star systems neutron-capture elements are synthesized in events such as r-process events and 
+population III supermassive stars undergoing s-processes nucleosynthesis ~\cite{Truran2002}. Population III stars are believed to exist in the 
+very early universe but have not been directly observed while r-process events can be observed from mergers of neutron stars or
+type II supernovae ~\cite{Truran2002}. The authors looked specifically at Sr and Ba for neutron capture elements. In figure ~\ref{fig:neutron_cap} 
+we see neutron-capture element abundances [Sr/H]
+and [Ba/H] for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars. The spread is quite wide with a number of stars having
+neutron-capture element abundances equal to, and even greater, than the Sun as well as stars with neutron-capture element abundances
+almost to [X/H] = -6. We can see that one of the SEGUE-1 stars observed in this study has a neutron-capture element abundance within
+[X/H] $\pm 0.5$ of our Sun while the other five observed in this study, as well as the one observed in a previous study, much lower at
+around [Sr/H] $\approx -5$ and [Ba/H] $\approx -4.5$. The total abundance of neutron capture elements within the lower six SEGUE-1 stars,
+five from this study plus one from the previous study, total to less than \(\sim 10^{-7} M_{\odot}\) for each element, which is orders
+of magnitude lower than the \(\sim 10^{-4} M_{\odot}\) released by a single neutron-capture element producing event. This low abundance
+indicates that aside from the neutron-capture elements released in the very early universe no other neutron-capture element synthesis
+occurred within SEGUE-1.
+
+\begin{wrapfigure}{r}{0.4\textwidth}
+    \begin{center}
+        \includegraphics[width=0.38\textwidth]{carbon.jpg}
+    \end{center}
+    \caption{Neutron-capture element abundance [Sr/H] and [Ba/H] within the six observed SEGUE-1 stars in this study 
+    (filled in red circles), one previously studied SEGUE-1 star (empty red circle), MW Halo stars (small black dots),
+    and the other candidate stars (cyan, green, and blue markers). The light dotted line at [X/H] = 0 represents the abundance
+    of the respective element within the sun and the bold dashed line represents the average abundance of the respective element
+    within the observed SEGUE-1 stars.}
+    \label{fig:carbon}
+\end{wrapfigure}
+
+In addition to confirming the age of the SEGUE-1 galaxy the authors also made some discoveries regarding chemical composition of early
+stars. Figure ~\ref{fig:carbon} shows the carbon abundance [C/H] for the observed SEGUE-1 stars as well as other candidate stars and
+MW Halo stars. We can see that 3 of the SEGUE-1 stars observed in this paper, as well as the one observed previously show enhanced levels
+of carbon. These carbon enhanced stars are observed to be the the four lowest mass stars out of the seven SEGUE-1 stars and indicates the
+importance of carbon in the enrichment process of early stars.
+
+Additionally the authors observed a large range of iron abundance within the SEGUE-1 stars spanning over two orders of magnitude between
+[Fe/H] = -1.4 to [Fe/H] = -3.8. this large range in combination with the relative consistency in metallicity of the stars indicates that
+the distribution of iron within the intergalactic and interstellar medium was inhomogeneous in the early universe, around the time of
+star formation within SEGUE-1
 
@@
 
-Future research points to observing a larger portion of SEGUE 1 stars. The six stars that were observed in this paper were deemed to
-be the brightest in the ultra faint dwarf galaxy and only allowed for a moderate S/N values between 20 and 46. In order to observe the other, dimmer,
-stars in SEGUE 1 we would require better telescopes to overcome the noise.
+Future research points to observing a larger portion of SEGUE 1 stars. The six stars that were observed in this paper, plus the 
+star observed in a previous study, were deemed to be the brightest in the ultra faint dwarf galaxy with magnitudes of $\sim 19$ mag.
+These seven SEGUE-1 stars were the only ones that scientists were able to capture sufficiently high resolution spectra for. These seven
+only represent a small sample
+
+\newpage
 

### 2021-06-11 Capstone/Semiconductor Materials for Ultra High Frequency Transistors.tex
Final paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Semiconductor Materials for\\Ultra High Frequency Transistors
    \thanks{University of Washington Bothell}
}

\author{\IEEEauthorblockN{Pongpak Techagumthorn}
    \IEEEauthorblockA{\textit{Physical Sciences Division} \\
        \textit{Univ. of Washington Bothell}\\
        Bothell, USA \\
        pongpakt@uw.edu}
}

\maketitle

\begin{abstract}
    Our modern day world is ever more reliant on connected devices. Inside every one of these devices there is a microprocessor
    inside. Currently the overwhelming majority of these microprocessors are constructed from silicon. As technology progresses
    we require ever faster processors. We are at a point now where we are reaching the limits of what silicon can provide. Scientists
    and engineers have turned to new semiconductor materials to overcome these limits. One such semiconductor material is Indium
    Gallium Phosphide (InGaP).

    This project aims to compare ultra-high frequency (0.3 - 3 GHz) characteristics of Silicon and Indium Gallium Phosphide in an
    LTSpice environment. For the transistor model we will be using the hybrid-$pi$ equivalent circuit transistor model.
    On the silicon side of things we will be simulating the general purpose 2N3904 NPN transistor. For the
    InGaP transistor we will be looking at the ERA-50SM+ device. Before simulating a complex device such as the ERA-50SM+ we started
    with small scale common emitter and common collector amplifier circuits. After running or small scale simulations we realized
    that the hybrid-$pi$ model was inadequate for our tests. Due to time constraints we were not able to come to a consensus
    for our research question.
\end{abstract}

\begin{IEEEkeywords}
    Transistors, Semiconductors, Silicon, InGaP, LTSpice
\end{IEEEkeywords}

\section{Introduction}

\subsection{Background}

\IEEEPARstart{E}{verywhere} we look more and more of our devices are being connected to the internet, from our phones
and computers to our cars and even our kitchen appliances. These so called "smart devices" are made
to accomplish a myriad of tasks but share one thing in common, they all have some sort of microprocessor
inside them to control what they do. Looking back at the history of microprocessors, and the transistors
that provided their building blocks, the prevailing semiconductor material used within these devices has
been silicon. The earliest transistors were constructed from germanium due to the ease of production at
a high purity monocrystalline form \cite{Early2001}. In the early 1950s a way to produce monocrystalline silicon was
developed and since then the industry has largely switched over to silicon. From the onset of transistor technology
scientists knew that silicon would be superior to germanium for transistors \cite{Jenkins2005}. The larger band gap in
silicon made silicon-based transistors more reliable and less susceptible to random noise from internal
and external sources \cite{Early2001,Jenkins2005}. The earliest, and most basic, transistors were bipolar junction transistors (BJTs).
These BJT devices consist of three semiconductor regions of alternating positive-negative-positive (PNP) or
negative-positive-negative (npn) doping, shown in fig. \cite{sze_physics_2007}. The two junctions allow small base input currents
to control much higher currents between the collector and emitter \cite{sze_physics_2007}. This allows BJTs to function
as either a swicth or an amplifier \cite{horowitz_art_2015}.

\begin{figure}[htbp]
    \centering
    \hspace*{\fill}
    \begin{subfigure}[b]{0.2\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/NPN.png}}
        \caption{NPN}
    \end{subfigure}
    \hspace*{\fill}
    \begin{subfigure}[b]{0.2\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/PNP.png}}
        \caption{PNP}
    \end{subfigure}
    \hspace*{\fill}
    \caption{Simplified internal construction, nomenclatures, and symbols of (a) NPN and (b) PNP transistors
    \\ Source: Adapted from \cite{sze_physics_2007}}
    \label{fig:transistor-block}
\end{figure}

In the past decade we have gotten closer and closer to the limits of silicon BJTs, especially in ultra high and
extremely high frequency applications that operate in the order of 1 – 100 GHz ($10^{9}$ Hz – $10^{11}$ Hz)
\cite{Schwierz2007}. One solution that scientists and engineers have tuned to is the use of newer semiconductor
materials. These new materials have electrical properties that are more suited for ultra high (UHF) to extremely high frequency (EHF)
applications and beyond \cite{Keyes2005}. Some new semiconductor materials that have already been implemented to
address these limitations include Indium and Gallium based semiconductor materials \cite{Schwierz2007}.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.5\textwidth]{figures/speed-of-light.jpeg}}
    \caption{Block diagram of the Aoki and Mitsui speed of light lab.
    The ERA-50SM+ device is part of the Pulsed Laser circuitry \\ Source: \cite{Aoki2008}}
    \label{fig:speed-of-light}
\end{figure}

An example of a device that makes use of Indium based transistors, specifically Indium Gallium Phosphide (InGaP),
is Kenichiro Aoki and Takahisa Mitsui's classic tabletop direct speed of light measurement lab \cite{Aoki2008}.The lab uses a
very high speed laser pulse and a detector to directly measure the speed of light, seen in fig. \ref{fig:speed-of-light} . Inside
the pulse circuit there is an ERA-50SM+ wide band monolithic amplifier that supports signals from DC up to 2 GHz \cite{ERA-50SM+}.
This amplifier uses a pair of NPN InGaP heterojunction bipolar transistors (HBT) in a Darlington pair, seen in fig.
\ref{fig:ERA-50SM}. HBTs function on the same principle as BJTs but instead of having the same semiconductor material at the 2 outer

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.3\textwidth]{figures/era50sm-schematic.png}}
    \caption{Simplified internal schematic of the ERA-50SM+ wide band monolithic amplifier \\ Source: \cite{ERA-50SM+}}
    \label{fig:ERA-50SM}
\end{figure}

Another solution that scientists and engineers use to overcome the limits of silicon BJTs is using faster switching transistor
technologies. Technologies such as  Field Effect Transistors (FET) are much better suited for these frequencies \cite{Schwierz2007}.
For this paper we choose to focus only on differing semiconductor materials in junction transistors, a superset of BJTs and HBTs,
since the ERA-50SM+ device exclusively uses this type of transistor.

\subsection{Purpose}

The goal of this project is to run simulations on InGaP HBTs and silicon BJTs and within an LTSpice environment to determine the more
suitable semiconductor material for ultra high frequency applications. Additionally we will also determine suitable applications for
each semiconductor material and the intrinsic electrical properties that make one semiconductor more suitable for ultra high frequency
applications over another.

\section{Methods}

\subsection{Evaluation Methods}

To evaluate the performance of the InGaP HBTs in comparison to standard silicon BJTs we will be simulating the ERA-50SM+ internal
circuit from fig. \ref{fig:ERA-50SM} within the manufacturer prescribed evaluation circuit, shown in fig. \ref{fig:ERA-Test-circuit}.
For the ERA-50SM+ device in fig. \ref{fig:ERA-Test-circuit} we will be constructing the internal circuitry as shown in fig. \ref{fig:ERA-50SM}
with both silicon and InGaP parameters

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.5\textwidth]{figures/era-test-circuit.png}}
    \caption{ERA-50SM+ evaluation circuit as prescribed by the manufacturer \\ Source: \cite{ERA-50SM+}}
    \label{fig:ERA-Test-circuit}
\end{figure}

Before simulating the entire ERA-50SM+ device in the prescribed evaluation circuit, fig. \ref{fig:ERA-Test-circuit} we will first
simulate each type of transistor within simple circuits. We will compare the simple circuit results to manufacturer provided
performance metrics to verify that the simulated components matches expected real world performance. For the silicon BJT model we will
be simulating the 2N3904 NPN BJT with parameters from KEC Semiconductor Corp \cite{3904}. For the InGaP HBT model we will be
determining parameters from literature \cite{Oka2001,Low1999} as we do not know the specific parameters for the HBTs within the
ERA-50SM+ device.

For the simple circuit testing we will be using basic common emitter and common collector transistor amplifier circuits,
fig. \ref{fig:NPN-CE-fig} and \ref{fig:NPN-CC-fig} respectively. The common emitter amplifier configuration produces a simple
voltage amplification circuit and the common collector circuit produces a simple current amplification circuit

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/NPN_CE-pic.png}}
        \caption{Common Emitter}
        \label{fig:NPN-CE-fig}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/NPN_CC-pic.png}}
        \caption{Common Collector}
        \label{fig:NPN-CC-fig}
    \end{subfigure}
    \caption{Simple NPN amplifier circuits \\ Source: \cite{horowitz_art_2015}}
\end{figure}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.4\textwidth]{figures/hybrid-pi.png}}
    \caption{Hybrid-$\pi$ equivalent circuit model for NPN transistors}
    \label{fig:hybrid-pi-model}
\end{figure}

\subsection{Hybrid-$\pi$ Model}

To model the transistor devices we will be using the hybrid-$\pi$ equivalent circuit model, shown in fig. \ref{fig:hybrid-pi-model}.
The hybrid-$\pi$ model was chosen since its parameters are easily calculated from information provided in component datasheets and
its relative accuracy in modeling junction transistor behavior across low and high frequencies \cite{Sharma1989,Malik1990}. This
model is able to function across a wide range of frequencies since it takes into account both basic parameters and parasitic
electrical properties of junction transistors \cite{Sharma1989}. The basic parameters needed for a simple hybrid-$\pi$ model are
the input resistance $r_\pi$, output resistance $r_0$, and the transconductance  $g_{m}v_{be}$ \cite{Malik1990}. These
three parameters are adequate for dc and low frequency simulations but for higher frequency simulations we need to add addition
parasitic elements. The base-emitter capacitance $c_\pi$, spreading resistance $r_x$, feedback resistance $r_\mu$, and interelectrode
capacitance $c_\mu$ compensate for high frequency effects within the stricture of the transistor \cite{Sharma1989}.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.4\textwidth]{figures/LTSpice-H-pi.png}}
    \caption{Hybrid-$\pi$ model in LTSpice}
    \label{fig:LTSpice-H-pi}
\end{figure}

\section{Analysis}

\subsection{LTSpice Models}

We used SPICE (Simulation Program with Integrated Circuit Emphasis) software to run our simulations, specifically the LTSpice
distribution by Analog Devices. The simulation setup in LTSpice consists of graphically laying out a circuit, assigning values
to the components, configuring simulation parameters, and running the simulation. fig. \ref{fig:LTSpice-H-pi} shows the
hybrid-$\pi$ model from fig. \ref{fig:hybrid-pi-model} set up in LTSpice. This model is not quite complete enough to run a 
simulation since the values of each component has not been assigned yet and there are no power and signal related components.

\subsubsection{Hybrid-$\pi$ model parameters}

\begin{table}[htbp]
    \centering
    \caption{Calculated parameters for hybrid-$\pi$ models}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Parameter & Si & InGaP & Unit\\
        \hline
        $g_m$ & $3.894 \times 10^{-2}$ & $1.073 \times 10^{-2}$ & $\mho$ \\
        $r_x$ & 580 & 53 & $\Omega$ \\
        $r_\pi$ & 6420 & 2609 & $\Omega$ \\
        $c_\pi$ & $1.666 \times 10^{-11}$ & $1.148 \times 10^{-14}$ & F \\
        $r_\mu$ & $15.12 \times 10^{6}$ & 11.01 & $\Omega$ \\
        $c_\mu$ & $4 \times 10^{-12}$ & $3.5 \times 10^{-15}$ & F \\
        $r_0$ & $2.522 \times 10^{5}$ & 10.93 & $\Omega$ \\
        \hline
    \end{tabular}
    \label{tab:h-pi_params}
\end{table}

To determine the values for each component we used calculations outlined by Malik \cite{Malik1990} and Ramanan
\cite{ramanan_functional_1985} with a combination of transistor h-parameters provided by manufacturer datasheets
for the 2N3904 \cite{3904}, and transistor t-parameters found in literature for the InGaP HBT\cite{Oka2001}.
Table \ref{tab:h-pi_params} lists the parameters that were calculated for the Si and InGaP hybrid-$\pi$ model. Worked out
calculations for these parameters are given in Appendixes \ref{appendix-Si} and \ref{appendix-InGaP}

\subsubsection{Simple Amplifier Circuits}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/LTSpice-CE.png}}
        \caption{Common Emitter}
        \label{fig:LTSpice-CE-fig}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}[b]{0.45\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/LTSpice-CC.png}}
        \caption{Common Collector}
        \label{fig:LTSpice-CC-fig}
    \end{subfigure}
    \caption{Simple NPN amplifier circuits in LTSpice}
\end{figure}

\begin{figure*}[htbp]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/Si-Result-CE.png}}
        \caption{Common Emitter Amplifier Results for Silicon. The vertical axis represents the voltage gain}
        \label{fig:Si-Result-CE}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}[b]{\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/Si-Result-CC.png}}
        \caption{Common Collector Amplifier Results for Silicon. The vertical axis represents the current gain}
        \label{fig:Si-Result-CC}
    \end{subfigure}
    \caption{Simple Amplifier Circuit Results for Silicon. The Vertical axis is the relative gain between the input signal and output load.
        The horizontal axis is the frequency. The bold black lines represent the 0 dB gain line in the vertical and the specified unity gain
        point in the horizontal.}
\end{figure*}

Before we could use these parameters in the full test circuits, fig. \ref{fig:ERA-50SM} and \ref{fig:ERA-Test-circuit}, we ran the
BJT/HBT models in simple amplifier circuits to ensure that they exhibit expected behavior. For this testing we are using common collector
ans common emitter amplifier circuits, fig. \ref{fig:NPN-CC-fig} and \ref{fig:NPN-CE-fig} from above. We then transferred the schematics
into LTSpice, fig. \ref{fig:LTSpice-CE-fig} and \ref{fig:LTSpice-CC-fig}, and determined the values for the external resistors, capacitors,
and voltage sources. The parameters for the external were calculated from Horowitz \cite{horowitz_art_2015}. For $V_{cc} = 10 V$ the external capacitor
and resistor values were: $R_1 = 88 k\Omega, R_2 = 110 k\Omega, R_E = 5 k\Omega, R_{Load} = 50 \Omega, C_1 = 47 \mu F, C_2 = 470 \mu F$.
For our first simulation run we set the $V_{signal}$ AC input to have an amplitude $0.1V$, a sufficiently low amplitude to stay within a small signal
model. We then ran an sinusoidal AC sweep between 1 Hz and 5 GHz ($5 \times 10^9$ Hz) to verify that we were seeing positive current/voltage gains
and that the unity gain frequencies, where the gain should be 0 dB, is close to the frequencies specified in the literature or datasheets.

\section{Results}

\subsection{Common Emitter and Common Collector Amplifier Simulations}

The silicon common emitter and common collector amplifier AC sweep results are shown in fig. \ref{fig:Si-Result-CE} and \ref{fig:Si-Result-CC}.
The results looked very promising at first. The common collector simulation had good level of gain and slowly ramped down to the unity gain
which was close to the specified value of 300 MHz. The common emitter simulation also showed decent levels of gain but missed the unity
gain mark by an order of magnitude. The silicon simulation results came out promising so we proceeded to the InGaP simulation.

The InGaP common collector and common emitter simulation results are shown in fig. \ref{fig:InGaP-Result-CE} and \ref{fig:InGaP-Result-CC}.
Unfortunately the results for this set of simulations was much less promising. We tried modifying the external component values, the input
signal amplitude but we still ended up with negative gains, or attenuations, in our InGaP simulation. Since this model should be showing at least
a positive gain we ran additional simulations to determine if our model was adequate for the simulations we are planning to run.

\begin{figure*}[htbp]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/InGaP-Result-CE.png}}
        \caption{Common Emitter Amplifier Results for InGaP. The vertical axis represents the voltage gain}
        \label{fig:InGaP-Result-CE}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}[b]{\textwidth}
        \centerline{\includegraphics[width=\textwidth]{figures/InGaP-Result-CC.png}}
        \caption{Common Collector Amplifier Results for InGaP. The vertical axis represents the current gain}
        \label{fig:InGaP-Result-CC}
    \end{subfigure}
    \caption{Simple Amplifier Circuit Results for Silicon. The Vertical axis is the relative gain between the input signal and output load.
        The horizontal axis is the frequency. As you can see both gains are in the negative region.}
\end{figure*}

\subsubsection{DC Analysis}

For our additional test to verify our model we chose to run some basic DC analysis simulations, specifically an analysis to characterize the
current-voltage curve of the transistor model. For our InGaP model we expect the curve to resemble that of fig. \ref{fig:InGaP-IV}. fig.
\ref{fig:InGaP-IV} shows the current at the collector, $I_C$, relative to the voltage between the collector and emitter, $V_{CE}$, of the
junction transistor. The several curves represents increasing input currents at the base, $I_B$, of the transistor in 10 $\mu A$ steps. This plot
shows that at very low collector-emitter voltages there is very little current gain but as the voltage increases the gain between the current
at the base and collector increases until a certain voltage, called the saturation voltage, where the collector current stays relatively constant
with increasing collector-emitter voltage. This type of behavior is exhibited by all junction based transistors \cite{sze_physics_2007}.

\begin{figure}[hbt!]
    \centerline{\includegraphics[width=0.25\textwidth]{figures/InGaP-IV.png}}
    \caption{The characteristic current-voltage curve of an InGaP HBT transistor. Notice how the collector current $I_C$ plateaus after around 0.5 - 0.6
    $V_{CE}$. \\ Source: \cite{Oka2001}}
    \label{fig:InGaP-IV}
\end{figure}

When we ran a DC analysis on the InGaP model to characterize it's current-voltage curve were given the result seen in fig. \ref{fig:InGaP-LT-IV}.
We can see that the model does show a steady rise in the collector current, $I_C$ plotted on the vertical axis, as the collector emitter voltage increases.
Where this model fell short is that there is no transition, at a saturation voltage, from the steady increase in the collector current to a plateau in the
collector current. From this result the hybrid-$\pi$ model seems to be inadequate for the series of tests we had planned to carry out.

\begin{figure}[hbt!]
    \centerline{\includegraphics[width=0.3\textwidth]{figures/InGaP-LT-IV.png}}
    \caption{DC simulation of the hybrid-$\pi$ InGaP model does not follow the plateau that is to be expected with an junction transistor}
    \label{fig:InGaP-LT-IV}
\end{figure}

\section{Conclusion}

Even though we were not able to reach a consensus on the performance of Silicon and InGaP junction transistors we were able to discover shortcomings in
the popular hybrid-$\pi$ equivalent circuit transistor model and paved the groundwork for future research with models that more accurately predict the
behavior of junction transistors.

\subsection{Limitations}

The biggest limitation that we had in this project was our choice of using the hybrid-$\pi$ model for our simulations. This model works on the assumption
that the junction transistor is purely a current amplifier device. In reality a junction transistor can be used as a current amplification device, but more
importantly, it is a device constructed from a pair of junctions between positively and negatively doped semiconductor material \cite{sze_physics_2007}.
This gives it properties such as the current-voltage curve and saturation voltage we saw from from fig. \ref{fig:InGaP-IV}. With this limitation we were
not able to simulate the circuits we originally planned. Another limitation that we had in this project is that we only chose to model a single type of
silicon BJT rather than sample a wide range to pick one that could possibly perform the best at ultra high frequencies. We were also limited in this project
by the fact that we were not able to find a specific InGaP HBT part that had a nicely formatted datasheet and specifications we could calculate our parameters
with. Instead we had to rely on research literature where the data was not as centralized. This meant that the data that we gathered may not be a very fair
comparison with InGaP HBTs in general or match very closely with the InGaP HBTs inside the ERA-50SM+ device.

\subsection{Future Work}

Some possible paths that could be taken for future work include developing a better simulation model to more accurately model the behavior of a junction
transistor, taking a wider sample of silicon BJTs to find more ultra high speed optimized types, and doing deeper research into InGaP HBTs to come up with
a better set of parameters. Developing a better simulation model for junction transistors will increase the accuracy of our results to the real world
behavior of junction transistors. Simulating a broader range of silicon transistors and digging deeper into InGaP transistor parameters will provide fairer
comparison between the two materials.

\appendices

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\section{Calculations for Silicon Hybrid-$\pi$ Model}
\label{appendix-Si}

Table \ref{tab:kec-3904} shows the data we gathered for the 2N3904 Silicon BJT parameters from KEC Semiconductor \cite{3904}.

\begin{table}[htbp]
    \centering
    \caption{Data gathered from KEC 3904 datasheet \\ Compiled from \cite{3904}}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Parameter & Value\\
        \hline
        $f_T$ & $300 \times 10^6$ Hz \\
        Unity Gain Frequency & \\
        \hline
        $I_C$ & 10V \\
        Collector Current at h-parameter test condition & \\
        \hline
        $h_{ie}$ & $7 \times 10^{3} \Omega$ \\
        Input Impedance & \\
        \hline
        $h_{re}$ & $4.25 \times 10^{-4}$ \\
        Voltage Feedback Ratio & \\
        \hline
        $beta = h_{fe}$ & 250 \\
        Small-Signal Current Gain & \\
        \hline
        $h_{oe}$ & $20.5 \times 10^{-6} \mho$ \\
        Collector Output Admittance & \\
        \hline
        $C_{ob} = C_{\mu}$ & $4 \times 10^{-12}$ F \\
        Collector Output Capacitance & \\
        \hline
    \end{tabular}
    \label{tab:kec-3904}
\end{table}

The following calculations use equations collected from \cite{Malik1990}.

To calculate the transconductance, $g_m$, we need the collector current at the h-parameter test condition, $I_C$, and the thermal
voltage, $V_T$.

\begin{equation}
    \begin{aligned}
        V_T &= \frac{kT}{q} \\
        V_T &= \frac{1.38 \times 10^{-28} \times 298.15}{1.602 \times 10^{-19}} \\
        V_T &= 0.02568V = 25.68 mV
    \end{aligned}
\end{equation}

where k is the Boltzmann Constant, T is the temperature in kelvin, and q is the charge of an electron

\begin{equation}
    \begin{aligned}
        g_m &= \frac{I_C}{V_T} \\
        g_m &= \frac{1 \times 10^{-3}}{0.02568} \\
        g_m &= 0.03894
    \end{aligned}
\end{equation}

To calculate the input resistance, $r_\pi$, we need the transconductance, $g_m$, and the small-signal current gain, $\beta = h_{fe}$.

\begin{equation}
    \begin{aligned}
        r_{\pi} &= \frac{\beta}{g_m} \\
        r_{\pi} &= \frac{250}{0.03894} \\
        r_{\pi} &= 6420
    \end{aligned}
\end{equation}

To calculate the feedback resistance, $r_{\mu}$, we need the input resistance, $r_{\pi}$, and the voltage feedback ratio, $h_{re}$.

\begin{equation}
    \begin{aligned}
        r_{\mu} &= \frac{r_{\pi}}{h_{re}} \\
        r_{\mu} &= \frac{6420}{4.25 \times 10^{-4}} \\
        r_{\mu} &= 15.12 \times 10^6
    \end{aligned}
\end{equation}

To calculate the output resistance, $r_0$, we need the collector output admittance, $h_{oe}$, small-signal current gain, $\beta = h_{fe}$,
and the feedback resistance, $r_{\mu}$.

\begin{equation}
    \begin{aligned}
        r_0 &= \left(h_{oe} - \frac{\beta}{r_{\mu}} \right)^{-1} \\
        r_0 &= \left(20.5 \times 10^{-6} - \frac{250}{15.12 \times 10^6} \right)^{-1} \\
        r_0 &= 2.522 \times 10^5
    \end{aligned}
\end{equation}

To calculate the spreading resistance, $r_x$, we need the input impedance, $h_{ie}$, and the input resistance, $r_{\pi}$.

\begin{equation}
    \begin{aligned}
        r_x &= h_{ie} - r_{\pi} \\
        r_x &= 7 \times 10^3 - 6420 \\
        r_x &= 580
    \end{aligned}
\end{equation}

To interelectrode capacitance, $c_{\pi}$, we need the transconductance, $g_m$, the unity gain frequency, $f_T$, and the
Collector Output Capacitance, $c_{\mu}$.

\begin{equation}
    \begin{aligned}
        c_{\pi} &= \frac{g_m}{2 \pi f_T} - c_{\mu} \\
        c_{\pi} &= \frac{0.03894}{2 \pi 300 \times 10^6} - 4 \times 10^{-12} \\
        c_{\pi} &= 1.666 \times 10^{-11}
    \end{aligned}
\end{equation}

\section{Calculations for InGaP Hybrid-$\pi$ Model}
\label{appendix-InGaP}

Table \ref{tab:InGaP-Params} shows the data we gathered for the InGaP parameters from T. Oka et al. \cite{Oka2001}.

\begin{table}[htbp]
    \centering
    \caption{Data gathered from T. Oka et al. \\ Compiled from \cite{Oka2001}}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Parameter & Value\\
        \hline
        $f_T$ & $114 \times 10^9$ Hz \\
        Unity Gain Frequency & \\
        \hline
        $h_{fe}$ & 28 \\
        Small-Signal Current Gain & \\
        \hline
        $r_e$ & $90 \Omega$ \\
        Emitter Resistance & \\
        \hline
        $r_b = r_x$ & $53 \Omega$ \\
        Base Resistance & \\
        \hline
        $r_c$ & $11 \Omega$ \\
        Collector Resistance & \\
        \hline
        $C_{\mu}$ & $3.5 \times 10^{-15}$ F \\
        Collector Capacitance & \\
        \hline
    \end{tabular}
    \label{tab:InGaP-Params}
\end{table}

Since the parameter we gathered are in t-parameter format we have to first convert them to h-parameters then to the values for
a hybrid-$\pi$ model

The following calculations use equations collected from Ramanan \cite{ramanan_functional_1985}.

To find our t-parameter $\alpha$ value we need the small signal current gain, $h_{fe}$.

\begin{equation}
    \begin{aligned}
        h_{fe} &= \frac{\alpha}{1 - \alpha} \\
        28 &= \frac{\alpha}{1 - \alpha} \\
        28 (1 - \alpha) &= \alpha \\
        28 &= 29 \alpha \\
        \alpha &= 0.9665
    \end{aligned}
\end{equation}

To find the input impedance, $h_{ie}$, we need the $\alpha$ value, the emitter resistance, $r_e$, and the base
resistance $r_b$.

\begin{equation}
    \begin{aligned}
        h_{ie} &= \frac{r_e}{1 - \alpha} + r_b \\
        h_{ie} &= \frac{90}{1 - 0.9655} + 53 \\
        h_{ie} &= 2662
    \end{aligned}
\end{equation}

To find the voltage feedback ratio, $h_{re}$, we need the $\alpha$ value, the emitter resistance, $r_e$, and the
collector resistance, $r_c$.

\begin{equation}
    \begin{aligned}
        h_{re} &= \frac{r_e}{\left(1 - \alpha\right) r_c} \\
        h_{re} &= \frac{90}{\left(1 - 0.9655\right) 11} \\
        h_{re} &= 237
    \end{aligned}
\end{equation}

To find the collector output admittance, $h_{oe}$, we need the $\alpha$ value and the collector resistance $r_c$

\begin{equation}
    \begin{aligned}
        h_{oe} &= \frac{1}{\left(1 - \alpha \right) r_c} \\
        h_{oe} &= \frac{1}{\left(1 - 0.9655\right) 11}
        h_{oe} &= 2.635
    \end{aligned}
\end{equation}

To find the transconductance, $g_m$, we need the small-signal current gain, $h_{fe}$, the input impedance, $h_{ie}$,
and the base resistance, $r_b = r_x$.

\begin{equation}
    \begin{aligned}
        g_m &= \frac{h_{fe}}{h_{ie} - rx} \\
        g_m &= \frac{28}{2662 - 53} \\
        g_m &= 0.01073
    \end{aligned}
\end{equation}

To calculate the input resistance, $r_\pi$, we need the input impedance, $h_{ie}$, and the base resistance, $r_b = r_x$.

\begin{equation}
    \begin{aligned}
        r_{\pi} &= h_{ie} - r_x \\
        r_{\pi} &= 2662 - 53 \\
        r_{\pi} &= 2609
    \end{aligned}
\end{equation}

To calculate the feedback resistance, $r_{\mu}$, we need the input impedance, $h_{ie}$, the base resistance, $r_b = r_x$, and
the voltage feedback ratio, $h_{re}$.

\begin{equation}
    \begin{aligned}
        r_{\mu} &= \frac{h_{ie} - r_x}{h_{re}} \\
        r_{\mu} &= \frac{2662 - 53}{237} \\
        r_{\mu} &= 11.01
    \end{aligned}
\end{equation}

To calculate the output resistance, $r_0$, we need the collector output admittance, $h_{oe}$, small-signal current gain, $h_{fe}$,
the input impedance, $h_{ie}$, the voltage feedback ratio, $h_{re}$, and the base resistance, $r_b = r_x$.

\begin{equation}
    \begin{aligned}
        r_0 &= \left(h_{oe} - \frac{h_{fe} h_{re}}{h_{ie} - r_x}\right)^{-1} \\
        r_0 &= \left(2.635 - \frac{(28)(237)}{2662 - 53}\right)^{-1} \\
        r_0 &= 10.93
    \end{aligned}
\end{equation}

\section*{Acknowledgment}

The author would like to thank Dr. S. Ramachandran for all the guidance and support for this project. The author would also like to thank
Dr. M. Gliboff and the UW Bothell physics class of 2021 for their support as well.

\bibliographystyle{IEEEtran}
\bibliography{bibliography}{}

\end{document}
